A Linear Inside-Outside Algorithm for Correcting Sequencing Errors in Structured RNA

### 2013-01-09 Recomb/results_RECOMB.tex
typo

\subsection{Implementation}
The software was implemented in Python2.7 using the \textit{mpmath}~\cite{mpmath} library
for  arbitrary floating point precision. The source code is freely available at: \\\hfill\verb+https://github.com/McGill-CSB/RNApyro+.

@@

\begin{table}[t]
\begin{center}
\begin{tabular}{lccc}
$|s|$&\multicolumn{3}{c}{Number of mutations}\\\cline{2-4}
		 			  & 6   &  12  & 24\\\cline{2-4}
100  				& 35s  & 238s & 1023s\\
300  			& 135s & 594s &2460s\\\cline{2-4}
		 						& 25   &    &	50		\\\cline{2-4}
500         & 5400s&       &  21003s    \\
\end{tabular}
\end{center}
\caption{Time to compute all probabilities. The first column indicates the length and  the column indexes indicate the number
 of mutations. $\alpha$ is
set at $0.5$,  $\beta$ to $1.5$ and $|\Omega|=44$.}
\label{tab:time}
\end{table}

@@

We designed our benchmark using a leave-one-out strategy. We randomly picked one sequence from our data set and performed $12$ random
mutations. Our sequences have $119$ nucleotides, thus the number of mutations corresponds to an error-rate of 10\%. We repeated this operation 
$10$ times. The value of $\beta$ has been set to $1.5$ (larger values gave similar results). To estimate the impact of the distribution of the weights
between the energy term and isostericity  score, we used 4 different values of $\alpha = {0, 0.5, 0.8, 1.0}$. Similarly, we also investigated the impact of 
an under- and over- estimate of the number of errors, and use values equal to 50\% (6 mutations) and 200\% (24 mutations) of the exact number of
errors (i.e. 12).

>>>>

\subsection{Implementation}
The software was implemented in Python2.7 using the \textit{mpmath}~\cite{mpmath} library
for  arbitrary floating point precision. The source code is freely available at: \\\verb+https://github.com/McGill-CSB/RNApyro+.

@@

\begin{table}[t]
\begin{center}
\begin{tabular}{lccc}
$|s|$&\multicolumn{3}{c}{Number of mutations}\\\cline{2-4}
		 			  & 6   &  12  & 24\\\cline{2-4}
100  				& 35s  & 238s & 1023s\\
300  			& 135s & 594s &2460s\\\cline{2-4}
		 						& 25   &    &	50		\\\cline{2-4}
500         & 5400s&       &  21003s    \\
\end{tabular}
\end{center}
\caption{Time to compute all probabilities. The first column indicates the length and  the column indexes indicate the number
 of mutations. $\alpha$ is
set at $0.5$,  $\beta$ to $15$ and $|\Omega|=44$.}
\label{tab:time}
\end{table}

@@

We designed our benchmark using a leave-one-out strategy. We randomly picked one sequence from our data set and performed $12$ random
mutations. Our sequences have $119$ nucleotides, thus the number of mutations corresponds to an error-rate of 10\%. We repeated this operation 
$10$ times. The value of $\beta$ has been set to $15$ (larger values gave similar results). To estimate the impact of the distribution of the weights
between the energy term and isostericity  score, we used 4 different values of $\alpha = {0, 0.5, 0.8, 1.0}$. Similarly, we also investigated the impact of 
an under- and over- estimate of the number of errors, and use values equal to 50\% (6 mutations) and 200\% (24 mutations) of the exact number of
errors (i.e. 12).
